Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-11 conclusion/conclusion.tex
New para

\chapter{Conclusion}

 [what is studied]

 [to what extend]

 [how good is the result]

@@

 [summary of the findings and advise]

 From this application, some suggestions on ABC SMC implementation could be drawn.

 [thanks]

>>>>

\chapter{Conclusion and future works}

%  [what is studied]

%  [to what extend]

%  [how good is the result]

@@

%  [summary of the findings and advise]

 From this application, some suggestions on ABC SMC implementation could be drawn. How to set the prior could be the most tricky decision for a high dimensional parameter inference. The distribution and the interval of each parameter can affect the inference results significantly and improper prior cold lead to poor fit. The epsilon trajectory and joint distribution of parameters can be used to identity possible local modes; if stuck, it takes much more samples than usual to jump out out local optimal. To avoid this a large population size and a proper epsilon schedule may help.for the uncertainties observed in model selection and some duplicated runs with high variance, a longer run with more generation could help to identify whether the convergency is consistent such that a reproducible inferred results can be obtained.

%  [thanks]

In terms of the future works, some more comparison with other algorisms could be of our interest. Least square fitting using MCMC \cite{ref:MCMC} and some other exact inference approaches could be performed on the same model and observed data, as the standard deviation at each measurement point is known. By comparing to these methods, differences in the inference results, algorithm robustness and required computational resources could be revealed and possibly help us in choosing an inference algorism that can balance the trade-off between efficiency and a reasonable good `fit'. Also there other implementation options of ABC SMC worth trying, e.g. CUDA acceleration and \verb|Julia| implementations\footnote[1]{\url{https://github.com/tanhevg/GpABC.jl}} \footnote[2]{\url{https://github.com/marcjwilliams1/ApproxBayes.jl}}.

In the aspect of models, some further models can be studied. If there were some more experimental evidence on the proposed interaction map, we could proposed more precise models, or calibrate some terms in our existing models. Also, models of other forms, e.g. PDE and stochastic models, could also be studied if a more complex model is needed for the dynamic system. Simplification is also possible of existing models
